DIAGNOSTIC SUPPORT OF SKIN LESION CLASSIFICATION USING CNN AND SOFT ATTENTION

### 2022-06-29 MDPI/Sensor Paper/template.tex
Update

%=================================================================
\documentclass[journal,article,submit,pdftex,moreauthors]{Definitions/mdpi} 
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

@@

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption

@@

% MDPI internal command: Title for citation in the left column
\TitleCitation{Title}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-0000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Khoi Do $^{1,\dagger,\ddagger}$\orcidA{}*}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{
$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}

@@

% Current address and/or shared authorship
\firstnote{Current address: 1st Dai Co Viet Street, Ha Noi, Viet Nam} 
\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Today, the rapid development of industrial zones leads to an increasing incidence of skin
	diseases because of polluted air. According to a report by the American Cancer Society, it is
	estimated that in 2022 there will be about 100,000 people suffered from skin cancer and more
	than 7600 of these people will not survive. In the context that doctors at provincial hospitals
	and health facilities are overloaded, doctors at lower levels have lack of experience, having
	a tool to support doctors in the process of diagnosing skin diseases quickly and accurately
	is essential. Along with the strong development of artificial intelligence technologies, many
	solutions and tools to support the diagnosis of skin diseases have been researched and
	developed. These include DenseNet, InceptionNet, ResNet, NasNet, SeNet, EfficientNet,
	VGGNet. In this study, another approach to build tools to aid in the diagnosis of skin
	pathologies is proposed. SOTA (state of the art) models DenseNet, InceptionNet, ResNet,
	NasNet, MobileNet combined with Soft-Attention are used as backbone. In addition,
	personal information such as age and gender are also used. In addition, a new loss function
	that takes into account the imbalance of the data is also proposed. Experimental results
	on dataset HAM10000 show that using InceptionResNetV2 with Soft-Attetion and new
	loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and aucscores of 0.81, 0.81, 0.82, and 0.989, respectively, are improvements compared to published
	indexes. Besides, using MobileNetV3Large combined with Soft-Attention and new loss
	function, even though the number of parameters is 11 times less, the number of floors is 4
	times less, it achieves 86 percent accuracy and 30 times faster diagnosis.}

% Keywords
\keyword{AI-enabled computer-aid diagnosis, Diagnosis, Skin Sancer, Skin Lesion
	Classification, Artificial Intelligence, Deep Learning, Machine Learning)}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{section}{-1} %% Remove this when starting to work on the template.
\section{How to Use this Template}

@@

% The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision

\section{Introduction}

The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper \cite{ref-journal}. Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}. Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences, Literature.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}

Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.

Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication.

Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
\begin{quote}
This is an example of a quote.
\end{quote}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
\subsection{Subsection}
\subsubsection{Subsubsection}

Bulleted lists look like this:
\begin{itemize}
\item	First bullet;
\item	Second bullet;
\item	Third bullet.
\end{itemize}

Numbered lists can be added as follows:
\begin{enumerate}
\item	First item; 
\item	Second item;
\item	Third item.
\end{enumerate}

The text continues here.

\subsection{Figures, Tables and Schemes}

All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, Table~\ref{tab2}, etc.

\begin{figure}[H]
\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
\caption{This is a figure. Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.\label{fig1}}
\end{figure}   
\unskip

\begin{table}[H] 
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CCC}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
Entry 1		& Data			& Data\\
Entry 2		& Data			& Data\\
\bottomrule
\end{tabularx}
\end{table}
\unskip

\begin{table}[H]
\caption{This is a wide table.\label{tab2}}
	\begin{adjustwidth}{-\extralength}{0cm}
		\newcolumntype{C}{>{\centering\arraybackslash}X}
		\begin{tabularx}{\fulllength}{CCCC}
			\toprule
			\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}     & \textbf{Title 4}\\
			\midrule
			Entry 1		& Data			& Data			& Data\\
			Entry 2		& Data			& Data			& Data \textsuperscript{1}\\
			\bottomrule
		\end{tabularx}
	\end{adjustwidth}
	\noindent{\footnotesize{\textsuperscript{1} This is a table footnote.}}
\end{table}

%\begin{listing}[H]
%\caption{Title of the listing}
%\rule{\columnwidth}{1pt}
%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
%\rule{\columnwidth}{1pt}
%\end{listing}

Text.

Text.

\subsection{Formatting of Mathematical Components}

This is the example 1 of equation:
\begin{linenomath}
\begin{equation}
a = 1,
\end{equation}
\end{linenomath}
the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.

This is the example 2 of equation:
\begin{adjustwidth}{-\extralength}{0cm}
\begin{equation}
a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
\end{equation}
\end{adjustwidth}

% Example of a page in landscape format (with table and table footnote).
%\startlandscape
%\begin{table}[H] %% Table in wide page
%\caption{This is a very wide table.\label{tab3}}
%	\begin{tabularx}{\textwidth}{CCCC}
%		\toprule
%		\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}	& \textbf{Title 4}\\
%		\midrule
%		Entry 1		& Data			& Data			& This cell has some longer content that runs over two lines.\\
%		Entry 2		& Data			& Data			& Data\textsuperscript{1}\\
%		\bottomrule
%	\end{tabularx}
%	\begin{adjustwidth}{+\extralength}{0cm}
%		\noindent\footnotesize{\textsuperscript{1} This is a table footnote.}
%	\end{adjustwidth}
%\end{table}
%\finishlandscape

% Example of a figure that spans the whole page width. The same concept works for tables, too.
\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=13.5cm]{Definitions/logo-mdpi}
\end{adjustwidth}
\caption{This is a wide figure.\label{fig2}}
\end{figure}

Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
%% Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

%% Example of a proof:
\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
\end{proof}
The text continues here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Patents}

This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

>>>>

%=================================================================
\documentclass[sensors,article,submit,pdftex,moreauthors]{Definitions/mdpi} 
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

@@

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
\usepackage{makecell}
\usepackage{placeins}
\usepackage{amsmath}
\usepackage{comment}

@@

% MDPI internal command: Title for citation in the left column
\TitleCitation{DIAGNOSTIC SUPPORT OF SKIN LESION
	CLASSIFICATION USING CNN AND SOFT
	ATTENTION}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0002-2566-5637} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Khoi Do Hoang$^{
		1,\dagger,%\ddagger
	}$\orcidA{}*}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)

\address{
$^{1}$ \quad Viet Dung Nguyen; dung.nguyenviet1@hust.edu.vn\\
$^{2}$ \quad Khoi Do Hoang; khoi.dh200332@sis.hust.edu.vn}

@@

% Current address and/or shared authorship
\firstnote{Current address: 1st Dai Co Viet Street, Ha Noi, Viet Nam} 
\secondnote{}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Today, the rapid development of industrial zones leads to an increased incidence of skin	diseases because of polluted air. According to a report by the American Cancer Society, it is estimated that in 2022 there will be about 100,000 people suffering from skin cancer and more than 7600 of these people will not survive. In the context that doctors at provincial hospitals and health facilities are overloaded, doctors at lower levels lack experience and having	a tool to support doctors in the process of diagnosing skin diseases quickly and accurately is essential. Along with the strong development of artificial intelligence technologies, many solutions and tools to support the diagnosis of skin diseases have been researched and developed. These include DenseNet, InceptionNet, ResNet, NasNet, SeNet, EfficientNet, VGGNet. In this study, another approach to building tools to aid in the diagnosis of skin pathologies is proposed. SOTA (state of the art) models DenseNet, InceptionNet, ResNet, NasNet, MobileNet combined with Soft-Attention are used as backbone. In addition, personal information such as age and gender are also used. In addition, a new loss function	that takes into account the imbalance of the data is also proposed. Experimental results on dataset HAM10000 show that using InceptionResNetV2 with Soft-Attention and new loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and AUC scores of 0.81, 0.81, 0.82, and 0.989, respectively, are improvements compared to published indexes. Besides, using MobileNetV3Large combined with Soft-Attention and new loss function, even though the number of parameters is 11 times less, the number of floors is 4 times less, it achieves 86 percent accuracy and 30 times faster diagnosis.}

% Keywords
\keyword{AI Diagnosis, Skin Sancer, Skin Lesion
	Classification, Deep Learning, Machine Learning)}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{section}{0} %% Remove this when starting to work on the template.
\begin{comment}
	\section{How to Use this Template}

@@

	% The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision
\end{comment}

\section{Introduction} 
\subsection{Problem Statement}
Skin cancer is one of the most common cancers leading to worldwide death. Every day, more than 9500\cite{03358} people in the United States are diagnosed with skin cancer. Otherwise, 3.6\cite{03358} million people are diagnosed with basal cell skin cancer each year. According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase\cite{11872}. In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States\cite{11872}. On the other hand, if patients are early diagnosed, the survival rate is correlated with 99 percent. However, once the disease progresses beyond the skin, survival is poor\cite{11872}. Moreover, with the increasing incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need for effective solution.

Recently, deep learning particularly, and machine learning in general algorithms have emerged to achieve excellent performance on various tasks, especially in skin disease diagnosis tasks. AI-enabled computer-aided diagnostics (CAD) has solutions in three main categories: Diagnosis, Prognosis, and Medical Treatment. Medical imaging, including ultrasound, computed tomography, magnetic resonance imaging, and X-ray image is used extensively in clinical practice. In Diagnosis, Artificial Intelligence (AI) algorithms are applied for disease detection to save progress execution before these diagnosis results are considered by a doctor. In Prognosis, AI algorithms are used to predict the survival rate of a patient based on his/her history and medical data. In Medical Treatment, AI models are applied to building solutions for a specific disease, medicine revolution is an example. In various studies, AI algorithms have provided various end-to-end solutions in the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging\cite{11872}.

In order to adapt the rise in skin cancer case, AI algorithms over the last decade has a great performance. Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{04861}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. Some of these models wich have been used as a backbone model in this paper will be discussed in the Related Work section.

\subsection{Related Works}
Skin lesion classification is not a new area, since there are many great performance models constructed. One of the most cutting-edge technologies that have been used is Soft-Attention as stated in\cite{03358}. Soumyyak et al construct several models formed by the combination of a backbone model including DenseNet201\cite{06993}, InceptionResNetV2\cite{00567}, ResNet50\cite{03385}\cite{05027}, VGG16\cite{1556} and Soft-Attention layer. Using those above backbones has been tried by many previous papers. Rishu Garg et al \cite{03798} uses transfer learning approach with CNN based model. Amirreaza et al \cite{10348} do not only use those above backbone model but also used InceptionV3\cite{00567} model. Another paper that uses the backbone models is \cite{09418}, Hemanth et al decide to use EfficientNet\cite{11946} and SeNET\cite{01507} instead and CutOut\cite{04552v2} method which involves creating holes of different sizes on the images i.e. technically making a random portion of image inactive during data augmentation process. \cite{01284} also used Deep Convolution Neural Network, Peng Yao et al used RandArgument which crops an image into several images from a fixed size, DropBlock which is used for regularization, Multi-Weighted New Loss which is used for dealing with the imbalanced data problem, end-to-end Cumulative Learning Strategy which can more effectively balance representation learning and classifier learning without additional computational cost. Another state of the art is GradCam and Kernel SHAP\cite{06612}, Kyle Young et al create model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification.

Otherwise, the Student and Teacher Model is also a state of the art in 2021\cite{03225}. The student and teacher model is created by Xiaohan Xing et al as the combination of two model which share the memory with each other. Therefore, they can take full advantage of what others learn. SkinLinkNet\cite{12602} and WonderM\cite{03426} are both tested the effect of segmentation on skin lesion classification problem created by Amirreza et al and Yeong Chan et al, respectively. Another approach is using metadata including gender, age, and capturing position as stated in \cite{03910} by Nil Gessert et al.

On the other hand, skin lesion classification problems are not only applied by Deep Learning but also Machine Learning. Random Forest, XGBoost, and Support Vector Machines are tested by \cite{03798} of Rishu Garg et al. Besides, Isolation Forest is applied before the soft-max activation of the deep learning model to detect out of distribution skin lesion images as stated in\cite{10348} by Amirreza Rezvantalab et al. Matrix Transformation, besides is also applied before the soft-max activation function in \cite{05045} by Michele Alberti et al. 
\begin{table}[ht]
	\centering
	\begin{tabular}{|c c c c c c c c c|} 
		\hline
		Class & AKIEC & BCC & BKL & DF & MEL & NV & VASC & Total \\ 
		\hline
		No. Sample & 327 & 514 & 1099 & 115 & 1113 & 6705 & 142 & 10015 \\
		\hline
	\end{tabular}
	\caption{Data Distribution in HAM10000}
	\label{table:1}
\end{table}

\subsection{Objectives}
In this paper, the effect of metadata on classifying skin disease is also analyzed .On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has the ability to classify in a balanced way between classes instead of well identifying the majority of classes.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}
\subsection{Data}
\subsubsection{Image Data}
The dataset used in this paper is the HAM10000 dataset published by Havard University Dataverse\cite{10417}. There are total 7 classes in this dataset containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), Basal cell Carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC). The distribution of the dataset is shown in the table below:
\FloatBarrier
\begin{table}[ht]
	\centering
	\begin{tabular}{|c c c c c c c c c|} 
		\hline
		Class & AKIEC & BCC & BKL & DF & MEL & NV & VASC & Total \\ 
		\hline
		No. Sample & 327 & 514 & 1099 & 115 & 1113 & 6705 & 142 & 10015 \\
		\hline
	\end{tabular}
	\caption{Data Distribution in HAM10000}
	\label{table:1}
\end{table}
\FloatBarrier
\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/DataDistribution}
	\caption{Example image of each class}
	\label{fig:datadistribution}
\end{figure}
More than 50 percent of lesions are confirmed through histopathology (HISTO), the ground truth for the rest of the cases is either follow-up examination (FOLLOWUP), expert consensus (CONSENSUS), or confirmation by in-vivo confocal microscopy (CONFOCAL). On the other hand, before being used for training the whole data is shuffled then split into two part. $90$ percent and $10$ percent of the data is used for training and validating respectively.

In the previous paper\cite{03358}, the image data is augmented for all class, the number of image increase to 18015 images. Since, this data is imbalanced, using augmented data may cause the problem of well classify on the majority of class. In this paper, instead of augmenting data, metadata is used. The way of processing metadata is discuss in MetaData section. Images in this dataset has the type of $RGB$ and shape of (450, 600). However, Each backbone need the different input size of image as well as the range of pixel value. DenseNet201\cite{06993} require the input pixels values are scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet dataset. In Resnet50 and Resnet152\cite{03385}\cite{05027}, the images are converted from $RGB$ to $BGR$, then each color channel is zero-centered with respect to the ImageNet dataset, without scaling. InceptionResNetV2\cite{11946}, on the other hand, will scale input pixels between $-1$ and $1$. Similarly, three versions of MobileNet\cite{04861}\cite{04381}\cite{02244}, NasNetMobile and NasNetLarge\cite{07012} require the input pixel is in range of $-1$ and $1$. 
\subsubsection{Metadata}
The HAM10000 dataset\cite{10417} also contain the metadata of patient including gender, age, and the capturing position. During the data exploration term, the age category miss 57 data points, which is decided to remove this 57 samples. In the gender and capturing position category contain some samples of unknown. Instead of removing, these "unknowns" data points is kept and considered as "prefer not to say". Besides, the label of the whole data is preprocessed into one-hot vector.
\subsection{Model Schema}
\subsubsection{Input Schema}
Using metadata as another input is not new. In paper\cite{03910}, they decide to keep the missing value and set its value to $0$. The sex and anatomical site are categorical encoded. The age, on the other hand is numerical normalized. After processing, the metadata is fed into a two-layer neural network with 256 neurons each. Each layer contains batch normalization, a ReLU\cite{08375} activation and dropout with $p = 0.4$. The network’s output is concatenated with the CNN’s feature vector after global average pooling. Especially, they use a simply data augmentation strategy to address the problem of missing values in metadata. During training, they randomly encode each property as missing with a probability of $p = 0.1$.

In this paper, the unknowns is kept as a type as discussed in Metadata section. Sex, anatomical site and age are also category encoded and numerical normalized, respectively. After processing, the metadata is then concatenated and fed into a dense layer of 4096 neurons. Finally, this this dense layer is then concatenate with the output of Soft-Attention which is then discussed in Soft-Attention section. The Input schema is described as follow:\\
\begin{figure}[h]
	\centering
	\includegraphics[width=0.7\linewidth]{"Definitions/Input Schema"}
	\caption{Input Schema}
	\label{fig:input-schema}
\end{figure}\\
Image data, on the other hand after being preprocessed, is fed directly into the backbone model. 
\subsubsection{Soft-Attention}
Applying the Soft-Attention layer in deep learning is not a new approach. Soft-Attention has been used in various applications: image caption generation in \cite{03044} and handwriting verification in \cite{202017} respectively. In skin lesion classification, Soft-Attention is used to increase the performance of the model as described in \cite{03358}. Soft-Attention can ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights. The function below describes the flow of the Soft-Attention module:
\[
f_{sa} = \gamma t\sum_{k=1}^{K}softmax(W_k * t)
\]

In order to apply Soft-Attention, there are two main steps. Firstly, the input tensor is put in grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map\cite{08513}. This feature map called $t \in R^{h \times w \times d}$ where $h, w, \text{and } d$ is the shape of tensor generated by a Convolution Neural Network(CNN), is then input to a 3D convolution layer whose weights is $W_k \in R^{h \times w \times d \times K}$. The output of this convolution is normalized using the softmax function to generate K = 16 attention maps. These $16$ attention maps are aggregated to produce a weight function called $\alpha$. This $\alpha$ function is then multiplied with feature tensor $t$ and scaled by $\gamma$, a learnable scalar. Finally, the out of Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention maps. 
\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/SoftAttention}
	\caption{Soft-Attention Module}
	\label{fig:softattention}
\end{figure}
In this paper, the Soft-Attention layer is applied in the same way in this paper\cite{03358}. The Soft-Attention module is described in the following diagram:
\FloatBarrier
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\linewidth]{Definitions/SoftAttentionBlock}
	\caption{Soft-Attention Module}
	\label{fig:softattentionblock}
\end{figure}
\FloatBarrier
\subsubsection{Backbone Model Architecture}
In this paper, the backbone models used in this paper are DenseNet201\cite{06993}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. The combination of DenseNet201, InceptionResNetV2 and Soft-Attention layer are both tested by the previous paper\cite{03358} with a great performance. Otherwise, Resnet50 also well classify but with much less number of parameter and depth than based on its f1-score and precision stated. Therefore, in this paper, the performance of the model Resnet152 and NasnetLarge which has the larger number of parameter and depth is analyzed. On the other hand, three version of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.  
\FloatBarrier
\begin{table}[ht]
	\centering
	\begin{tabular}{|c | c c c|} 
		\hline
		Model & Size(MB) & Parameters & Depth \\ 
		\hline
		Resnet50 & 98 & 25.6M & 107 \\ 
		\hline
		Resnet152 & 232 & 60.4M & 311 \\ 
		\hline
		DenseNet201 & 80 & 20.2M & 402 \\
		\hline
		InceptionResNetV2 & 215 & 55.9M & 449 \\
		\hline
		MobileNet & 16 & 4.3M & 55 \\ 
		\hline
		MobileNetV2 & 14 & 3.5M & 105 \\ 
		\hline
		MobileNetV3Small & Unknown & 2.5M & 88 \\ 
		\hline
		MobileNetV3Large & Unknown & 5.5M & 118 \\
		\hline
		NasnetMobile & 23 & 5.3M & 308 \\
		\hline
		NasnetLarge & 343 & 88.9M & 533 \\ 
		\hline
	\end{tabular}
	\caption{Size and Parameters and Depth of backbone model used in this paper}
	\label{table:2}
\end{table}
\FloatBarrier

\subsubsection{Model}
The whole architecture of the model used for image feature extraction is applied in the same way in paper \cite{03358}. Metadata branch, otherwise is preprocessed before feeding into a dense layer then concatenate with the output of Soft-Attention layer. It is described in the figure below:
\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/MainModel}
	\caption{Overall Model Architecture}
	\label{fig:mainmodel}
\end{figure}

\subsection{Loss Function}
The loss function used in this paper is categorical cross-entropy. Consider $X = [x_1, x_2, \dots, x_n]$ as the input feature, $\theta = [\theta_1, \theta_2, \dots, \theta_n]$. Let $N$, and $C$ is the number of training examples and number of class respectively. The categorical cross-entropy loss is presented as:
\[L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N}W_c\times y^c_n \times \log(\hat{y}^c_n)\]
where $\hat{y}^c_i$  is the output of model and $y^c_i$ is the target that the model should return, $W_c$ is the weight of class $c$. Since the dataset face the imbalanced problem then I applied the class weight for the loss. This formula below is used to calculate the class weight:
\[W = N \odot D\]
\[D = \begin{bmatrix}
	\frac{1}{C \times  N_1} & \frac{1}{C \times  N_2} & \dots & \frac{1}{C \times  N_n}\\
\end{bmatrix} = \frac{1}{C} \odot \begin{bmatrix}
	\frac{1}{N_1} & \frac{1}{N_2} & \dots & \frac{1}{N_n}\\
\end{bmatrix}\]
where $N$ is the number of training sample, $C$ is the number of class, $N_i$ is the number of sample in each class $i$. $D$ is the matrix contain the inverse of $C \times N_i$. 
\subsection{Evaluation Metrics}
\begin{figure}[!htb]
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=1.1\linewidth]{Definitions/Confusion-matrix}
		\caption{Confusion Matrix}\label{Fig:Data1}
	\end{minipage}\hfill
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=.7\linewidth]{Definitions/AUC}
		\caption{Area Under the Curve}\label{Fig:Data2}
	\end{minipage}
\end{figure}
In this paper, the model is evaluated by using the confusion matrix and related metrics. The figure 4 illustrates the presentation of a $2 \times 2$ confusion matrix used for $2$ class. Consider a confusion matrix $A$ with $C$ number of class. Let $A^i$ and $A^j$ is the set of $A$ rows and columns respectively. 
\[
A = \begin{bmatrix}
	a_{11} & a_{12} & \dots & a_{1j} \\
	a_{21} & a_{22} & \dots & a_{2j} \\
	\vdots & \vdots	&  & \vdots\\
	a_{i1} & a_{i2} & \dots & a_{ij} 
\end{bmatrix}
\]

The True Positive(TP) of all class in this case is the main diagonal of the matrix $A$. The following method are used to calculate the False Positives(FP), False Negatives(FN), and True Negatives(TN) of all class:
\[
FP = -TP + \sum_{k=1}^{i}A^i_k \hspace{1cm} FN = -TP + \sum_{k=1}^{j}A^j_k
\]
\[
TN_c = \sum_{i=1}^{C}\sum_{j=1}^{C}a_{ij} - \left[ \sum_{k=1}^{i}A^i_{i=c k} + \sum_{k=1}^{j}A^j_{j=c k} \right] + a_{i=c j=c} \implies TN = \begin{bmatrix}
	TN_1 & TN_2 & \dots & TN_c
\end{bmatrix}
\]
Then, the model is evaluated by the following metrics:
\[\text{Sensitivity(Sens)} = \frac{TP}{TP + FN} \hspace{1cm} \text{Specificity(Spec)} = \frac{TN}{TN + FP}\]
\[\text{Precision} = \frac{TP}{TP + FP} \hspace{1cm} \text{F1 Score} = \frac{2 \times TP}{2 \times TP + FP + FN + TN}\]
\[\text{Accuracy} = \frac{TP + TN}{TP + FP + FN + TN} \hspace{1cm} \text{Balanced Accuracy} = \frac{\text{Sens} + \text{Spec}}{2}\]
The last metric is the $AUC$ score standing for Area Under the Curve which is the Receiver Operating Curve(ROC) that indicate the probability of TP versus the probability of FP.  
\subsection{Traning}
Before training, the dataset is split into three sub datasets including training, validation, and testing. In this paper, the graphic card that is used to train is Nvidia RTX TitanV.\\
All the model in this paper is trained with Adam Optimizer\cite{6980}. The initial learning rate is set to $0.001$, an learning rate reduction schedule is setup with the minimum learning rate is $0.0000001$ with the factor of $0.2$, the epsilon argument of the optimizer is set to $0.1$. On the other hand, Early Stopping is also set up, if the accuracy of validation set dose not increase after 25 epochs, the training will stop.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
The accuracy of all model is presented in the figure below:
\begin{table}[h]
	\centering
	\begin{tabular}{| c | c | c | c |}
		\hline
		InceptionResNetV2 & DenseNet201 & ResNet50 & VGG16 \\
		\hline
		0.93 & 0.91 & 0.92 & 0.88\\
		\hline
	\end{tabular}
	\caption{Accuracy of the model with augmented data}
	\label{table:3}
\end{table}
\begin{table}[h]
	\centering
	\begin{tabular}{| c | c | c | c | c |}
		\hline
		InceptionResNetV2 & DenseNet201 & ResNet50 & Resnet152 & MobileNetV2\\
		\hline
		0.89 & 0.89 & 0.70 & 0.57 & 0.81\\
		\hline
	\end{tabular}
\end{table}
\begin{table}[h]
	\centering
	\begin{tabular}{| c | c | c | c |}
		\hline
		MobileNetV3Large & MobileNetV3Small & NasNetLarge & NasNetMobile\\
		0.84 & 0.78 & 0.86 & 0.86\\
		\hline
	\end{tabular}
	\caption{Accuracy of the model with metadata}
	\label{table:4}
\end{table}
